---
title: "Sampling App"
author: "David Monarres"
date: "March 29, 2019"
output: html_document
runtime: shiny
---
# Introduction

We will use this little app to collect some random samples from our class data. 

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
class_data <- read_csv("Data/s19-survey_nooutliers.csv", 
    col_types = cols(baseball = col_factor(levels = c("A's", 
        "Giants")), cig = col_factor(levels = c("Yes", 
        "No")), football = col_factor(levels = c("49ers", 
        "Raiders")), gender = col_factor(levels = c("Female", 
        "Male")), love_stats = col_factor(levels = c("Yes", 
        "No")), math190 = col_factor(levels = c("Yes", 
        "No")), mj = col_factor(levels = c("Yes", 
        "No"))))
create_histogram <- function(df, vari){
    p <- ggplot(df, aes_string(x=vari)) + geom_histogram(bins=10, fill="white", color="black")
    return(p)
}
```

```{r, echo=FALSE}
selectInput(label = "Choose Variable: ",choices = c("height", "distance"), inputId = "var",selected = "distance")

numericInput(min = 1,max=100, step=1, inputId = "sample_size",value = 5,label = "Sample Size: ")


renderPlot(create_histogram(class_data, input$var))
```

The mean of the population that you are sampling from is `r reactive(print(round(mean(class_data[[input$var]]),1)))`

The standard deviation of the population that you are sampling from is `r reactive(print(round(sd(class_data[[input$var]]),1)))`

Get a sample:
```{r, echo=FALSE}
actionButton("sample","Sample")
```

The sample that you just took is:
```{r, echo=FALSE}
reactive(
  if(input$sample >0){
    class_sample <- class_data[[input$var]][sample(1:length(class_data[[input$var]]),  input$sample_size)]
    print(class_sample)
    print("The mean of this sample is:")
    print(round(mean(class_sample),1))
    print("The sd of this sample is:")
    print(round(sd(class_sample),1))
  }
)
```


Take the means on your table and enter them into the spreadsheet here:

<a href="https://docs.google.com/spreadsheets/d/1WkL3yacfHnoRDSKbnY_bP0FcuJ8-RMmMSIdwLy99vVI/edit?usp=sharing" target="_blank">Spreadsheet</a>